---
title: "DailyMeanMax"
author: "LRA"
date: "01/02/2019"
output: github_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
library(lubridate)
Month_order <- c("January","February","March","April","May","June","July","August","September","October","November","December")
```
## Analysis of temperature logger data
AK: 3 HOBO loggers, deployed ~May-Aug 2019. Note, the loggers were NOT deployed on the NSFWD transects but at nearby locations.  
WA: 30 loggers deployed, 23 files recovered across 5 sites. Loggers were deployed on the NSFWD transects. June-July 2019 at most sites, June-Aug 2019 at Beach Haven (WA.C).  
OR: 9 files from 4 sites, June-Oct 2019
BB: 11 files from 6 sites, July-Aug 2019
```{r import and clean,include=FALSE}
AK_full <- read.csv("AK.2019.alltemps.csv")
AK_full$DateObs <- as.character(AK_full$DateObs)
AK_full$DateObs <- as.POSIXct(AK_full$DateObs,format="%m/%d/%y   %H:%M")
AK_full$Day <- floor_date(AK_full$DateObs,unit = "day")
AK_full$Month <- floor_date(AK_full$DateObs,unit="month")
AK_full$Month.w <- as.character.Date(AK_full$Month,format="%B")
AK_full$Month.w <- ordered(AK_full$Month.w,levels=Month_order)

AK_summ <- AK_full %>%
  group_by(Region, SiteCode,SiteName,TidalHeight,Month,Day)%>%
  summarise(DailyMean=mean(TempC),DailyMax=max(TempC),
            DailySD=sd(TempC),
            DailySE=sd(TempC)/sqrt(length(TempC)))
AK_summ$Month.w <- as.character.Date(AK_summ$Month,format="%B")
AK_summ$Month.w <- ordered(AK_summ$Month.w,levels=Month_order)

WA_full <- read.csv("WA.2019.alltemps.csv")
WA_full$DateObs <- as.character(WA_full$DateObs)
WA_full$DateObs <- as.POSIXct(WA_full$DateObs,format="%m/%d/%y   %H:%M")
WA_full$Day <- floor_date(WA_full$DateObs,unit = "day")
WA_full$Month <- floor_date(WA_full$DateObs,unit="month")
WA_full$Month.w <- as.character.Date(WA_full$Month,format="%B")
WA_full$Month.w <- ordered(WA_full$Month.w,levels=Month_order)

WA_summ <- WA_full %>%
  group_by(Region, SiteCode,SiteName,TidalHeight,Month,Day)%>%
  summarise(DailyMean=mean(TempC),DailyMax=max(TempC),
            DailySD=sd(TempC),
            DailySE=sd(TempC)/sqrt(length(TempC)))
WA_summ$Month.w <- as.character.Date(WA_summ$Month,format="%B")
WA_summ$Month.w <- ordered(WA_summ$Month.w,levels=Month_order)

OR_full <- read.csv("OR.alltemps.2019.csv")
OR_full$DateObs <- as.character(OR_full$DateObs)
OR_full$DateObs <- as.POSIXct(OR_full$DateObs,format="%m/%d/%y   %H:%M")
OR_full$Day <- floor_date(OR_full$DateObs,unit = "day")
OR_full$Month <- floor_date(OR_full$DateObs,unit="month")
OR_full$Month.w <- as.character.Date(OR_full$Month,format="%B")
OR_full$Month.w <- ordered(OR_full$Month.w,levels=Month_order)

OR_summ <- OR_full %>%
  group_by(Region, SiteCode,SiteName,TidalHeight,Month,Day)%>%
  summarise(DailyMean=mean(TempC),DailyMax=max(TempC),
            DailySD=sd(TempC),
            DailySE=sd(TempC)/sqrt(length(TempC)))
OR_summ$Month.w <- as.character.Date(OR_summ$Month,format="%B")
OR_summ$Month.w <- ordered(OR_summ$Month.w,levels=Month_order)

BB_full <- read.csv("BB.alltemps.2019.csv")
BB_full$DateObs <- as.character(BB_full$DateObs)
BB_full$DateObs <- as.POSIXct(BB_full$DateObs,format="%m/%d/%y   %H:%M")
BB_full$Day <- floor_date(BB_full$DateObs,unit = "day")
BB_full$Month <- floor_date(BB_full$DateObs,unit="month")
BB_full$Month.w <- as.character.Date(BB_full$Month,format="%B")
BB_full$Month.w <- ordered(BB_full$Month.w,levels=Month_order)

BB_summ <- BB_full %>%
  group_by(Region, SiteCode,SiteName,TidalHeight,Month,Day)%>%
  summarise(DailyMean=mean(TempC),DailyMax=max(TempC),
            DailyMed=median(TempC),DailySD=sd(TempC),
            DailySE=sd(TempC)/sqrt(length(TempC)))
BB_summ$Month.w <- as.character.Date(BB_summ$Month,format="%B")
BB_summ$Month.w <- ordered(BB_summ$Month.w,levels=Month_order)
```
## Daily Mean Temperatures  
```{r mean temps, echo=FALSE}
AK_meanp <- ggplot(AK_summ,aes(x=SiteName,y=DailyMean,fill=TidalHeight))+geom_boxplot()+
  facet_wrap(~Month.w)+
  scale_fill_manual(values=c("royalblue","lightblue"))+
  ylab("Daily Mean Temp (ºC)")+
  xlab("Site")+
  labs(title="AK 2019 Temps")+
  theme_bw()+
  theme(panel.background = element_rect(color="black"),
        strip.background = element_rect(color="black",fill="white"),
        axis.text.x=element_text(angle=90))
AK_meanp
WA_meanp <- ggplot(WA_summ,aes(x=SiteName,y=DailyMean,fill=TidalHeight))+geom_boxplot()+
  facet_wrap(~Month.w)+
  scale_fill_manual(values=c("royalblue","lightblue"))+
  ylab("Daily Mean Temp (ºC)")+
  xlab("Site")+
  labs(title="WA 2019 Temps")+
  theme_bw()+
  theme(panel.background = element_rect(color="black"),
        strip.background = element_rect(color="black",fill="white"),
        axis.text.x=element_text(angle=90))
WA_meanp
OR_meanp <- ggplot(OR_summ,aes(x=SiteName,y=DailyMean,fill=TidalHeight))+geom_boxplot()+
  facet_wrap(~Month.w)+
  scale_fill_manual(values=c("royalblue","lightblue"))+
  ylab("Daily Mean Temp (ºC)")+
  xlab("Site")+
  labs(title="OR 2019 Temps")+
  theme_bw()+
  theme(panel.background = element_rect(color="black"),
        strip.background = element_rect(color="black",fill="white"),
        axis.text.x=element_text(angle=90))
OR_meanp
BB_meanp <- ggplot(BB_summ,aes(x=SiteName,y=DailyMean,fill=TidalHeight))+geom_boxplot()+
  facet_wrap(~Month.w)+
  scale_fill_manual(values=c("royalblue","lightblue"))+
  ylab("Daily Mean Temp (ºC)")+
  xlab("Site")+
  labs(title="BB 2019 Temps")+
  theme_bw()+
  theme(panel.background = element_rect(color="black"),
        strip.background = element_rect(color="black",fill="white"),
        axis.text.x=element_text(angle=90))
BB_meanp
```  
  
Mean temperatures show slight differences between the upper and lower transects, larger differences between sites within regions and across regions  

## Daily Max Temperatures  
```{r max temps, echo=FALSE}
AK_maxp <- ggplot(AK_summ,aes(x=SiteName,y=DailyMax,fill=TidalHeight))+geom_boxplot()+
  facet_wrap(~Month.w)+
  scale_fill_manual(values=c("royalblue","lightblue"))+
  ylab("Daily Max Temp (ºC)")+
  xlab("Site")+
  labs(title="AK 2019 Temps")+
  theme_bw()+
  theme(panel.background = element_rect(color="black"),
        strip.background = element_rect(color="black",fill="white"),
        axis.text.x=element_text(angle=90))
AK_maxp
WA_maxp <- ggplot(WA_summ,aes(x=SiteName,y=DailyMax,fill=TidalHeight))+geom_boxplot()+
  facet_wrap(~Month.w)+
  scale_fill_manual(values=c("royalblue","lightblue"))+
  ylab("Daily Max Temp (ºC)")+
  xlab("Site")+
  labs(title="WA 2019 Temps")+
  theme_bw()+
  theme(panel.background = element_rect(color="black"),
        strip.background = element_rect(color="black",fill="white"),
        axis.text.x=element_text(angle=90))
WA_maxp
OR_maxp <- ggplot(OR_summ,aes(x=SiteName,y=DailyMax,fill=TidalHeight))+geom_boxplot()+
  facet_wrap(~Month.w)+
  scale_fill_manual(values=c("royalblue","lightblue"))+
  ylab("Daily Max Temp (ºC)")+
  xlab("Site")+
  labs(title="OR 2019 Temps")+
  theme_bw()+
  theme(panel.background = element_rect(color="black"),
        strip.background = element_rect(color="black",fill="white"),
        axis.text.x=element_text(angle=90))
OR_maxp
BB_maxp <- ggplot(BB_summ,aes(x=SiteName,y=DailyMax,fill=TidalHeight))+geom_boxplot()+
  facet_wrap(~Month.w)+
  scale_fill_manual(values=c("royalblue","lightblue"))+
  ylab("Daily Max Temp (ºC)")+
  xlab("Site")+
  labs(title="BB 2019 Temps")+
  theme_bw()+
  theme(panel.background = element_rect(color="black"),
        strip.background = element_rect(color="black",fill="white"),
        axis.text.x=element_text(angle=90))
BB_maxp
```  
  
Daily maximum temps are higher and more variable in Washington.
More intra-region variability in Bodega.